Create data sets for modeling

### 2016-07-14 portfolio/analysis/3-createData_linear_modeling.Rmd
Group the gear strategies by permit holder - year

# hand edited with groups:
gears <- readr::read_csv("../../data/gear-strategies.csv")
# adds gear strategy column:
cfecnew <- left_join(cfecnew, select(gears, p_gear, gear_group))
```

>>>>

# hand edited with groups:
gears <- readr::read_csv("../../data/gear-strategies.csv")
gears <- mutate(gears, p_gear = 
  ifelse(nchar(p_gear) == 1, paste0("0", p_gear), p_gear))
# adds gear group column:
cfecnew$gear_group <- NULL
cfecnew <- left_join(cfecnew, select(gears, p_gear, gear_group))

topstrategies_gear <- group_by(cfecnew, p_holder, year) %>%
  summarize(strategy_gear = paste(sort(unique(gear_group)), collapse = ", ")) %>%
  as_data_frame()
rev(sort(table(topstrategies_gear$strategy_gear)))[1:50]

cfecnew <- left_join(cfecnew, topstrategies_gear) # adds gear strategy column

# xx <- filter(topstrategies_gear, strategy_gear == "")
# filter(cfecnew, p_holder == 138, year == 1990) %>% as.data.frame()
```
